Data Preparation

### 2019-01-09 Data Preparation.Rmd
Determining AoD met with assessments

##Course Manual 
We create a dataframe from the Corpus:
```{r}

>>>>

### AoD from Assessment Type
In order to determine which AoD each course covers with its assessments, we need to create a binary matrix which indicates which AoD(s) each assessment type covers. We have created such matrix on our google drive and we save it in the following piece of code as `map_assessment_AoD`. `map_assessment_AoD` indicates that, for instance, the assessment type `Essay` covers the AoD `Critical Thinking Skills`, `Communication Skills` and `Writing Skill`.
```{r}
map_assessment_AoD <- as.matrix(gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=719531216')[,lists$AoD] %>%
                                  mutate_all(as.logical))
rownames(map_assessment_AoD) <- lists$Assessment
print(map_assessment_AoD[1:5, 8:12])
```

Now that we have the matrix `map_assessment_AoD`, we create the tibble `d_assessment_clean` which only contains the assessments that are covered by each course and we loop through its rows to determine which AoD, each assessment covers. In the loop, we first extract the row of `d_assessment_clean` and save it as `observation` and determine the corresponding assessment which we save as `assessment`. Then we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
```{r}
d_AoD_assessment <- tibble(Code        = character(0),
                           Assessment  = character(0),
                           AoD         = character(0))

for(i in 1 : nrow(d_assessment)){

  observation <- d_assessment[i, ]

  assessment  <- observation$Assessment
  AoD_covered <- map_assessment_AoD[assessment, ]
  AoD         <- lists$AoD[AoD_covered]

  if(length(AoD) >= 1){ # if no AoD are covered by assessment (e.g. written exam), then do not rbind rows to d_AoD_assessment
      AoD_assessment_tidy <- cbind(observation, AoD) %>%
    as_tibble
      d_AoD_assessment <- rbind(d_AoD_assessment, AoD_assessment_tidy)
  }

}

print(d_AoD_assessment)
```

Similarly to what we did with the tibble `d_AoD_ILO`, we first eliminate the AoD that are not covered by the assessments and then we take the unique combination of course and AoD in case a course had several assessments covering the same AoD.
```{r}
d_AoD_assessment <- d_AoD_assessment %>%
  select(Code, AoD) %>%
  unique
print(d_AoD_assessment)
```

## Course Manual 
We create a dataframe from the Corpus:
```{r}
